### 2024-06-20 Paper/MSEPM-Manuscript.tex
Update MSEPM-Manuscript.tex
changes for everything in email besides figure changes and exponential distribution

Provided a trained MSEPM model and an unobserved methylation matrix, epigenetic factors are estimated by calculating each independent OLS for solution all $i$ 
sites given the $r_{i,k}$ coefficients set for the respective input factor.  These epigenetic factors can then be used to find the expected methylation value 
using the trained individual site models where $$E[m_{i,j}] = r_{i,0} + P_{j} \dot R_{i}$$

@@

Methylation sites were simulated by first randomly setting the dynamic range of the methylation site, 
$-1< \delta < 1$ a site intercept, $r^0_i$, and the site error, $\sigma_i \sim \mathcal{U}(0.025, 0.05)$. The dynamic 
range of the methylation site is described by the initial methylation value, $m_0 ~ \beta(.2,.2)$, 
and the target methylation value, $m_t$, where the dynamic range is $\delta_i = m_t - m_o$.
The value of $m_t$ is set conditionally to ensure dynamic range is always larger than some specified threshold, $\theta$, where 
$ \theta \leq|\delta| \geq. r^0_i ~ \beta(.2,.2)$.

Simulated methylation sites are then randomly associated with a combination of zero, one, or multiple epigenetic factors. Rates for sites 
associated with multiple factors were set by sampling from a uniform distribution. The weighted factor rates are normalized so 
the input combination of traits describes the dynamic range of the simulated site, $\delta$. If a site is associated 
with no factors the observed methylation status of a site is described by a random normal with a characteristic offset, $\hat{m_i} = r_{0,i} + N(\mu, \sigma)$.

>>>>

Provided a trained MSEPM model and an unobserved methylation matrix, epigenetic factors are estimated by calculating each independent OLS for solution all $i$ 
sites given the $r_{i,k}$ coefficients set for the respective input factor.  These epigenetic factors can then be used to find the expected methylation value 
using the trained individual site models where $$E[m_{i,j}] = r_{i,0} + P_{j} \dot R_{i}$$ where $P_{j} \dot R_{i}$ is a matrix of point values p and r.

@@

Methylation sites were simulated by first randomly setting the possible range of the methylation site, 
$-1< \delta < 1$ a site intercept, $r^0_i$, and the site error, $\sigma_i \sim \mathcal{U}(0.025, 0.05)$. The 
range of the methylation site is described by the initial methylation value, $m_0 ~ \beta(.2,.2)$, 
and the target methylation value, $m_t$, where the range is $\delta_i = m_t - m_o$. $\beta(.2,.2)$ is the beta distribution with its parameters for randomly setting the sample.
The value of $m_t$ is set conditionally to ensure possible range is always larger than some specified threshold, $\theta$, where 
$ \theta \leq|\delta| \geq. r^0_i ~ \beta(.2,.2)$.

Simulated methylation sites are then randomly associated with a combination of zero, one, or multiple epigenetic factors. Rates for sites 
associated with multiple factors were set by sampling from a uniform distribution. The weighted factor rates are normalized so 
the input combination of traits describes the range of the simulated site, $\delta$. If a site is associated 
with no factors the observed methylation status of a site is described by a random normal with a characteristic offset, $\hat{m_i} = r_{0,i} + N(\mu, \sigma)$.
